---
title: "Advance r lab 4"
author: HUSSNAIN & ARFAN
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Import Libraries:

```{r setup}
library(tidyverse)
library(cowplot)
```

Linear regressions functions to calculate some functions:

```{r linreg}
linreg <- setRefClass("linreg",fields = list(regressionsCoefficients = "matrix",
                                    fittedValues = "numeric",
                                    residuals = "matrix",
                                    degreesOfFreedom = "numeric",
                                    residualVariance = "numeric",
                                    varianceRegressionCoefficients = "matrix",
                                    tValuesForEachCoefficient = "matrix",
                                    pValues = "matrix",
                                    call = "formula",
                                    dataA = "character"),
                      methods = list(

                                      initialize = function(formula, data) {
                                        modelMatrixX <- as.matrix(model.matrix(formula, data))
                                        modelMatrixY <- as.matrix(data[all.vars(formula)[1]])

                                        .self$regressionsCoefficients <- (solve(t(modelMatrixX) %*% modelMatrixX)) %*% (t(modelMatrixX) %*% modelMatrixY)

                                        .self$fittedValues <- as.vector(modelMatrixX %*% regressionsCoefficients)

                                        .self$residuals <- modelMatrixY - fittedValues

                                        .self$degreesOfFreedom <- nrow(data) - ncol(modelMatrixX)

                                        .self$residualVariance <- as.numeric((t(residuals) %*% residuals) / degreesOfFreedom)

                                        .self$varianceRegressionCoefficients <- as.numeric(residualVariance) * (solve(t(modelMatrixX) %*% modelMatrixX))

                                        isPositive <- function(x) x>=0

                                        .self$tValuesForEachCoefficient <- as.vector(regressionsCoefficients) / (sqrt(abs(varianceRegressionCoefficients)))

                                        .self$pValues <- pt(-abs(tValuesForEachCoefficient), degreesOfFreedom)

                                        .self$call <- formula

                                        .self$dataA <- deparse(substitute(data))
                                      },

                                      print = function() {
                                       printA(.self)
                                      },

                                      pred = function() {
                                        res <- predA(.self)
                                        return(res)
                                      },

                                      plot = function() {
                                        plotA(.self)
                                      },

                                      coef = function() {
                                        coefA(.self)
                                      },

                                      resid = function() {
                                        residA(.self)
                                      },

                                      summary = function() {
                                        summaryA(.self)
                                      }
                                    ))
```


##Functions

Test data iris

``` {r}
data(iris)
linreg_mod <- linreg$new(Petal.Length~Species, data = iris)
```

coef function shows regression coefficients in linreg:

``` {r}
coefA <- function(data) {
  return(data$regressionsCoefficients)
}

linreg_mod$coef()
```

plot function shows graphical reperentation:

```{r}
plotA <- function(data) {
  stR <- sqrt(abs(data$residuals / sqrt(abs(data$residualVariance))))
  df <- data.frame(data$residuals, data$fittedValues, stR)
  plot1 <- ggplot(df, aes(x = data.fittedValues, y = Petal.Length)) +
    geom_point(shape = 1) +
    labs(title = "Residuals vs Fitted Values",
         x = "Fitted Values", y = "Residuals") +
    stat_summary(fun = median, color = "red", geom = "line")

  plot2 <- ggplot(df, aes(x = data.fittedValues, y = Petal.Length.1)) +     geom_point(shape = 1) +
    labs(title = "Scale-Location",
         x = "Fitted Values",
         y = expression(sqrt(Standardized~residuals))) +
    stat_summary(fun = mean, color = "red", geom = "line")

  plot_grid(plot1, plot2, ncol = 1, nrow = 2)
}

linreg_mod$plot()
```

pred function shows fitted values in linreg:

```{r}
predA <- function(data) {
  fitValue <- data$fittedValues
  return(fitValue)
}

linreg_mod$pred()
```

print function shows linear regression coefficients:

```{r}
printA <- function(data) {
  cat("Call:\n")
  print(paste0("linreg(formula = ", format(data$call), ", data = ", data$dataA, ")"))
  cat("\nCoefficients:\n")
  print(as.data.frame(t(data$regressionsCoefficients)))
}

linreg_mod$coef()
```


resid function shows residual in linreg:

```{r}
residA <- function(data) {
  rd <- data$residuals
  return(rd)
}


linreg_mod$resid()
```

summary function shows summary of linreg:

```{r}
summaryA <- function(data) {
  stars <- function(value) {
    switch (value < 0.001, return("***"))
    switch (value < 0.01, return("**"))
    switch (value < 0.05, return("*"))
    switch (value < 0.1, return("."))
    return(" ")
  }
  e <- as.vector(data$regressionsCoefficients)
  pValues <- as.vector(diag(data$pValues))
  mat <- matrix(e)
  se <- sqrt(as.vector(diag(data$varianceRegressionCoefficients)))
  mat <- cbind(mat, se)
  mat <- cbind(mat, diag(as.matrix(data$tValuesForEachCoefficient)))
  mat <- round(mat, 5)
  mat <- cbind(mat, pValues)
  mat <- cbind(mat, sapply(pValues, stars))
  colnames(mat) <- c("Estimate", "Std. Error", "t-values", "p-values", " ")
  matDF <- as.data.frame(mat)
  cat("Call: \n")
  cat("linreg(formula = ", paste0(data$call), ", data =", data$dataA,")")
  cat("\n\n")
  cat("Coefficients: \n")
  print(matDF)
  cat("Residual standard error:", sqrt(data$residualVariance),"on", data$degreesOfFreedom,"degrees of freedom")
}

linreg_mod$summary()

```


